\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-30 latex/paper_sensores/paper.tex
termine

\begin{itemize}
\item Sensitivity variation of the accelerometer: $\pm 0.01 \%/^\circ C$
\item Offset variation of the accelerometer: $\pm 1.2mg/^\circ C \approx 0.012m s^{-1}$
\item Sensitivity variation of the gyroscope: No information is provided. 
\item Offset variation of the gyroscope: $\pm 40 ^\circ s^{-1} \approx 0.70 rad s^{-1}$
\end{itemize}

@@

In Figure \refp{fig:bajada} two different magnitudes
are shown at the same time: the three projections of the acceleration and the
temperature vs. time, thus two axes are needed to be shown: on left side
the acceleration in ms−2, and on right side the temperature in
$^oC$.\\

>>>>

\begin{itemize}
\item Sensitivity variation of the accelerometer: $\pm 0.01 \%/^\circ C$
\item Offset variation of the accelerometer: $\pm 1.2mg/^\circ C \approx 0.012m s^{-1}$
\item Sensitivity variation of the gyroscope: No information is provided. 
\item Offset variation of the gyroscope in the whole operating range ($-40^\circ C$ to $85^\circ C$): $\pm 40 ^\circ s^{-1} \approx 0.70 rad s^{-1}$
\end{itemize}

@@

In Figure \refp{fig:bajada} two different magnitudes
are shown at the same time: the three projections of the acceleration and the
temperature vs. time, thus two axes are needed to be shown: on left side
the acceleration in $ms{−2}$, and on right side the temperature in
$^oC$.\\
